\section*{Summary and Conclusion}

There are some aspects of user interface design that both the Stanford and MIT
websites do particularly well. For example, both of the sites have exceptional
search engines. We found that we could find anything on the sites by using
these search engines, and we found the familiar Google output pleasing to
read. Neither of the search engines are perfect, but these imperfections were
mostly subjective stylistic choices.

The Stanford site excels at consistency. Until you get near the very bottom of the
site hierarchy, you can tell that you are on a Stanford page just by the use of
color and page layout alone. The Stanford University brand is reinforced by the
use of Stanford's colors in text and controls, as well as the tasteful images
of the university's campus. Interestingly, \textbf{MIT and Stanford have the
same university colors}. You wouldn't know this by visiting the MIT site, as
every page uses a different color scheme, and even the home page changes its
scheme every day.

One issue where MIT suffered greatly relative to Stanford was in site consistency. The MIT site was entirely inconsistent. The
home page was styled in one way, the page(s) for each department were styled in another way, and the individual sites for people
were styled differently. Beyond this, there was a clear distinction in the quality of the design of the webpages between portions
of the site which the designers thought were likely to be visited often and those parts which were not. The portions of the site
where people were likely to visit were incredibly complex and reasonably well thought out (see \url{https://sfs.mit.edu/}),
but they stood in such contrast to the utterly minimal effort (see \url{http://web.mit.edu/philosophy/}) put in on designing other portions of the sight that they made the overall navigation experience worse. In order to fix their consistency
issues, the designers of the MIT site should establish guidelines for colorschemes, layouts, and make a consistent header and
footer to go on every page. This would not be that difficult to implement assuming a reasonable site design system. If on the other
hand, the site was designed in an entirely decentralized way, they could at least use a consistent logo and require similar colors.

The juxtaposition of the different portions of the site which happened while investigating the site emphasized just how bad parts
of the site are by occasionally reminding the user how well designed pages look. Some of the pages (e.g.
\url{http://www.eecs.mit.edu/}) on the EECS (Electrical Engineering and Computer Science) department's portion of the
site were so poorly designed as to be unreadable.

During our time spent on the MIT website, we learned that \textit{community
matters to MIT}. This was obvious by the liberal use of headshots of people in
the MIT community on many of the site's pages. With this in mind, MIT handles
this emphasis exceptionally well. Images of people are very high quality and
have text captions and often \texttt{alt} attributes for each. Even the faculty
pages (for example, the faculty and advisors for the computer science department:
\url{https://www.eecs.mit.edu/people/faculty-advisors}) have images of most if
not all of the names on the page.

Stanford also includes images of faculty, staff, and students, but many less
than MIT. For example, Stanford's computer science faculty page
(\url{http://cs.stanford.edu/directory/faculty}) is a long list of names
with no images whatsoever. Even where there are images on Stanford's site,
there is a severe lack of accessibility features for them. Apart from those
on the home page, images on the Stanford site do not have tooltips, text
captions, or \texttt{alt} attributes.

Both the Stanford and MIT sites lacked any discernable indication of one's position within their respective hierarchies.
There was no way to know what the parent page to the current page was, let alone trace the path down the hierarchy back to
the home page. This made it so it was impossible to travel back to the current page's parent without using the browser's back
button. This issue, while seemingly trivial, made navigation much more difficult as it was incredibly easy to dive down the
hierarchy while looking for somethinkg, but then the only way to step back up to a previous level in the hierarchy was by returning
to the home page and starting the descent again.
